\documentclass{beamer}

% Custom alert environment
\newenvironment{myalert}{\begin{itemize}
[<+-| alert@+>]
}
{\end{itemize}}


% Slide Theme
\usetheme{Singapore}

% Change alert color to blue
\setbeamercolor{alerted text}{fg=blue}

% Font Size
\setbeamerfont{frametitle}{size=\huge}
\setbeamerfont{itemize/enumerate body}{size=\huge}
\setbeamerfont{itemize/enumerate subbody}{size=\huge}


% Title Page
\title{\huge Research Skills for CBAs and DML Class}
\author{}
\date{\today}

\begin{document}

% Title Slide
\begin{frame}
  \titlepage
\end{frame}

% Slide 1: Learning Intentions
\begin{frame}{\huge Learning Intentions}
  \begin{myalert}
    \item To efficiently search for information
    \item To evaluate the credibility of sources
  \end{myalert}
\end{frame}

% Slide 2: Search Tips
\begin{frame}{\huge Search Tips}
  \begin{myalert}
    \item Use \textbf{quotation marks} for specific phrases.
    \item Use \textbf{+} to combine terms (e.g., "Climate Change" + "Impact").
    \item Use \textbf{-} to exclude terms (e.g., "Climate Change" - "Politics").
  \end{myalert}
\end{frame}

% Slide 3: Reliable Sources
\begin{frame}{\huge Reliable Sources}
  \begin{myalert}
    \item Prefer websites with \textbf{.edu}, \textbf{.gov}, or \textbf{.org} domains.
    \item Be cautious with \textbf{.com} sites as they may be biased.
  \end{myalert}
\end{frame}

% Slide 4: Evaluating Sources (CARRDSS Method)
\begin{frame}{\huge Evaluating Sources: CARRDSS}
  \begin{myalert}
    \item \textbf{Credibility}: Who is the author? Have they written on the topic before?
    \item \textbf{Accuracy}: Can facts be verified by other reputable sources?
    \item \textbf{Reliability}: Is there bias? Is it factual or opinionated?
    \item \textbf{Relevance}: Does it answer your research question?
    \item \textbf{Date}: Is it current?
    \item \textbf{Source}: Are reliable sources cited?
  \end{myalert}
\end{frame}

% Slide 5: Activity - Research Exercise
\begin{frame}{\huge Activity - Research Exercise}
  \textbf{\huge Task:}
  \begin{myalert}
    \item Pick a topic and start searching using the tips we’ve discussed.
    \item Evaluate one source using the CARRDSS method.
  \end{myalert}
\end{frame}

% Slide 6: Example Topics
\begin{frame}{\huge Example Topics}
  \begin{myalert}
    \item "How does climate change affect polar bears?"
    \item "What is the relationship between technology and mental health?"
  \end{myalert}
\end{frame}

% Slide 7: Using Microsoft Forms
\begin{frame}{\huge Using Microsoft Forms}
  \textbf{\huge Submit Your Findings:}
  \begin{myalert}
    \item Fill out the Microsoft Form to submit your research results.
  \end{myalert}
\end{frame}

\end{document}
